The Power of Liberty in the American Workplace: Unveiling the Global Impact of Free Will Perceptions on Job Satisfaction

### 2024-02-14 outputs/paper/paper.qmd
data section outline

# Introduction
In the evolving landscape of organizational psychology, the exploration of individual agency beliefs (particularly free will) and their impact on job satisfaction presents a compelling field of study. "Agency Beliefs Over Time and Across Cultures: Free Will Beliefs Predict Higher Job Satisfaction" by Feldman et al. embarks on this journey, unveiling the nuanced relationship between one's belief in free will and their subsequent job satisfaction across diverse cultural contexts. A focused exploration of this relationship within the context of the American workforce provides a valuable estimand, given the United States' strong emphasis on individualism, autonomy, and the freedom to shape one's destiny which are principles deeply ingrained in the national ethos.

The paper addresses a significant gap in existing literature by articulating how free will beliefs, beyond serving as philosophical contemplations, exert a tangible influence on individuals' professional lives. Through a robust approach that includes longitudinal studies and cross-cultural analyses, the research highlights a consistent positive correlation between strong beliefs in free will and higher levels of job satisfaction. This relationship, significantly influenced by perceived autonomy, underscores the pivotal role of individual agency beliefs in the context of the American workplace, where personal freedom and self-determination are highly valued.

The importance of this paper lies not only in its findings but also in its implications, offering practical insights for enhancing organizational culture and employee satisfaction within the American context. By highlighting the importance of fostering environments that champion autonomy and respect individual agency beliefs, the paper prompts business leaders and policymakers to rethink strategies for workplace management and development. This shift towards recognizing and nurturing free will beliefs could serve as a key lever for boosting job satisfaction, employee engagement, and organizational performance across the United States.

Structurally, the paper unfolds starting from its comprehensive methodology (including the six-month study of American online workers) to its extensive cross-cultural survey, which contextualizes the American data within a global framework. It then articulates the specific implications of free will beliefs for job satisfaction among American employees, weaving these insights into broader discussions on the interplay between cultural values, individual beliefs, and workplace dynamics. The concluding sections propose future research directions and practical applications, emphasizing the critical role of understanding and leveraging individual agency beliefs in cultivating a more motivated and satisfied workforce.

You can and should cross-reference sections and sub-sections.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

>>>>

# Introduction

In recent years, the intersection between personal beliefs in free will and cognitive behavioral outcomes has emerged as a pivotal area of psychological inquiry. While the existence of free will is a highly theoretical and philosophical question, the belief in free will has undeniable effects on various other psychological constructs such as autonomy, meaningfulness, and self-efficacy (@baumeister2014, @alquist2013). Despite the robustness of these relationships, there remain gaps in the literature of the specific dynamics of these effects and the generalizability in field settings. @feldman2017 conducted a study investigating the effects of the belief in free will on job satisfaction and attempted to draw cross-cultural and longitudinal conclusions on the positive correlation between the belief in free will and job satisfaction.

They executed three distinct studies: the first with real estate agents in Taiwan over three months, the second involving American workers over six months using Amazon Mechanical Turk, and the third utilizing a large cross-cultural sample from the World Values Survey encompassing 16 countries. This multifaceted approach allowed them to assess the generalizability of free will beliefs as predictors of job satisfaction across various cultural contexts and professional environments, providing a robust examination of how these beliefs influence job satisfaction over time.

Utilizing the same dataset and a similar methodology to Feldman et al. (2017), we aim to replicate their results in the context of the United States, a very heterogenous country that is characterized by a high importance of individualist, but also cultural diversity and socioeconomic inequality. While Feldman et al. did investigate the relationship between the belief in free will and job satisfaction in the United States, they did not integrate these results to the cross-cultural analysis, as the US were not included in the sample of 16 countries. This paper, therefore, seeks to fill this gap and reproduce these aspects of the Feldman et al. paper: (1) the relationship between the belief in free will and job satisfaction applies to the context of American adults working at Amazon Mechanical Turk (2) free will is a significant predictor of job satisfaction at the national-level, using the World Values Survey. The estimand is the correlation between the belief in free will and job satisfaction. Our reproduction was conducted using the statistical programming language R (@citeR). In the data analysis and visualization process, we also made use of the following R packages: tidyverse (@citetidyverse), dplyr (@citedplyr), knitr (@citeknitr), kableExtra (@citekExtra), and countrycode (@citecc).

We begin our paper with a closer look at the data source and measurement (@sec-data), followed by a selection of relevant results (@sec-results). Finally, we will conclude with a discussion of our findings to integrate our replication with the original paper by @feldman2017 and the broader literature on free will beliefs. We will also discuss potential ethical biases, limitations, and future directions. This shift towards recognizing and nurturing free will beliefs could serve as a key lever for boosting job satisfaction, employee engagement, and organizational performance across the United States. ### TALK ABOUT FINDINGS HERE###

# Data {#sec-data}
## Source {#sec-source}
Dataset Overview:

Introduction to the Dataset: Start by providing a brief overview of the dataset(s) used, including the source (e.g., Amazon Mechanical Turk, World Values Survey) and the rationale for selecting these datasets for replication.
Scope and Scale: Mention the size of the dataset, the number of participants, and the time frame covered by the data collection.
## Measurement {#sec-measurement}
Variables Description:

Dependent Variable(s): Describe the main variable of interest, job satisfaction, including how it was measured or operationalized in the dataset.
Independent Variable(s): Explain the measurement of free will beliefs and any other relevant variables that were analyzed as predictors or controls in the study (e.g. job autonomy, self-efficacy etc.)

Covariates and Controls: If applicable, detail any additional variables used as controls or covariates in your analysis, such as demographic information, employment characteristics, or cultural factors.

GO INTO GREAT DETAIL WITH MEASUREMENT!

## Data Characteristics {#sec-characteristics}

Preprocessing Steps: Outline the steps taken to prepare the data for analysis, including any cleaning, filtering, or transformation processes.
Handling of Missing Data: Describe how missing data were addressed, whether through imputation, exclusion, or another method.

Summary Statistics and Initial Observations:

Descriptive Statistics: Provide summary statistics for the main variables, including means, standard deviations, and ranges. This gives readers a sense of the data's central tendencies and variability.
Visualizations: Include graphs or tables that offer an initial view of the data, such as distributions of job satisfaction and free will beliefs. Discuss any notable patterns or preliminary observations.
Comparative Analysis (if applicable):

Comparison with Original Study: If you have access to summary statistics or data visualizations from the Feldman et al. study, briefly compare those findings with your dataset to highlight similarities or differences.
Rationale for Differences: Discuss any expected or surprising differences in the data between the original study and your replication effort, potentially attributable to cultural or temporal differences.

#####
